Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
review Formal Verification of Linear Digital Controllers

Researchers in formal verification methods of control systems have studied
various effects of discretising the dynamics, including delayed
response~\cite{Duggirala2015}, and Finite Word Length (FWL) constraints with
the objective to either verify (eg.  \cite{daes20161}) or optimise
(eg.~\cite{oudjida2014design}) implementations.  There are in fact two
different problems arising from FWL effects.  The first corresponds to the
error in the dynamics caused by the inability of the hardware to represent
the exact dynamics of the system whilst the second relates to rounding
errors during computation.  In \cite{fialho1994stability} a stability
measure based on the error of the digital dynamics ensures that the FWL
errors do not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  Most papers following this line of verification focus on
finding a correct implementation of a known desired controller, looking for
optimal parameter representations using FWL but ignoring the effects of
rounding errors due to issues of mathematical tractability.  The analyses
in~\cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Pogramming (SDP).  Whilst the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases the SDP solver uses floating point arithmetic and soundness is checked
by upper bounding the error.
An alternative approach is taken by \cite{park2016scalable}, where the verification of existing
code is performed against a known model by extracting an LTI model of the
code through symbolic execution. In order to account for rounding errors, an
upper bound is introduced in the verification phase. If the error of the implementation
is lower than this tolerance level, then the verification is successful.

>>>>

Researchers in formal verification of control systems have studied
various effects of discretising the dynamics, including delayed
response~\cite{Duggirala2015}, and Finite Word Length (FWL) constraints with
the goal to either verify ({\it e.g.},  \cite{daes20161}) or optimise
({\it e.g.},~\cite{oudjida2014design}) implementations.  There are in fact two
different problems arising from FWL effects.  The first corresponds to the
error in the dynamics caused by the inability of the hardware to represent
the exact dynamics of the system whilst the second relates to rounding
errors during computation.  In \cite{fialho1994stability} a stability
measure based on the error of the digital dynamics ensures that the FWL
errors do not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  Most studies following this verification research field focus on
finding a correct implementation of a known desired controller, looking for
optimal parameter representations using FWL, but ignoring the effects of
rounding errors due to issues of mathematical tractability.  The analyses
in~\cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Pogramming (SDP).  Whilst the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is checked
by upper bounding the error.
An alternative approach is taken by \cite{park2016scalable}, where the verification of existing
code is performed against a known model by extracting an LTI model of the
code through symbolic execution. In order to account for rounding errors, an
upper bound is introduced in the verification phase. If the error of the implementation
is lower than this tolerance level, then the verification is successful.
